Non-analogues in paleoecological reconstruction

### 2015-07-24 Paper_Markdown.Rmd
Added pandoc/knit header.

---
output: pdf_document
---
Non-analogues in paleoecological reconstruction - the effects of analogue distance
========================================================

>>>>

---
title: "Non-analogues in paleoecological reconstruction"
author: "Simon Goring *et al*."
date: '`r format(Sys.time(), ''%d %B, %Y'')`'
output:
  pdf_document:
    pandoc_args: -V geometry:vmargin=1in -V geometry:hmargin=1in
  md_document:
    variant: markdown_github
  word_document:
    fig_height: 6
    fig_width: 6
csl: ecology.csl
pandoc_args: -H margins.sty
bibliography: non-analogue_clim.bib
---
Non-analogues in paleoecological reconstruction - the effects of analogue distance
========================================================
